{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-07 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

    % ===================================================================================

@@

                0 &\le F(z) - F(\bar x) + \frac{L}{2}\Vert z - x\Vert^2 - \frac{L}{2}\Vert^2 z - \bar x\Vert^2. 

@@

                \Vert \mathcal G_{L_k} y_k\Vert 

@@

                &= -\alpha_k^{-1}L_k^{-1}(\mathcal G_{L_k}(y_k)). 

@@

            For all $k \ge 1$ let $\hat L = \max_{i = 0, 1, \ldots, k} L_k$ then 

@@

                    \frac{\alpha_0 \sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{\hat L^{-1}}

@@

                    1 + \frac{1}{2}\alpha_0 \sqrt{L_0}k\sqrt{\hat L^{-1}}

@@

                    1 + \frac{k\alpha_0\sqrt{L_0 \hat L^{-1}}}{2}

@@

                    \sqrt{L_0^{-1}\hat L} + \frac{k\alpha_0}{2}

@@

                L^{-1}_0\hat L\left(

@@

                = \frac{4\hat L}{L_0(2 + k \alpha_0)^2}. 

@@

@@

    \section{Algorithmic description of GMAPG}
        There are several components to the GMAPG algorithm. 
        This section will introduce various type of implementations that can be fitted into GMAPG in Definition \ref{def:generic-mapg-ls}. 
            \begin{algorithmic}[1]\label{alg:armijo-ls}
                    % \textbf{Function ArmijoLS}
                    % $(f, g, x, v, L, \alpha, \_, \_)$
                    \textbf{Function ArmijoLS:}
                    \begin{tabular}{ll}
                        $f : \RR^n \rightarrow \RR$ & Convex Lipschitz smooth\\ 
                        $g: \RR^n \rightarrow \overline \RR$  &  Convex function with Proximal operator\\ 
                        $x \in \RR^n$ & Vector\\
                        $v \in \RR^n$ & Vector\\
                        $L \in \RR$ & $L > 0$\\
                        $\alpha \in \RR$  & $\alpha \in (0, 1]$
                    \end{tabular}

@@

                \STATE{$\alpha^+ := (1/2)\left(\alpha\sqrt{\alpha^2 + 1} - \alpha^2\right)$.}
                \STATE{$y^+ := \alpha^+ v + (1 - \alpha^+)x$.}
                \STATE{$L^+ := L$. }
                \FOR{$i = 1, 2,\ldots, 53$}
                    \STATE{$L^+ := 2L^+$. }
                    \STATE{$x^+ := T_{1/L^+, f, g}(y^+)$. }
                    \IF{$D_f(x^+, y^+) \le (L^+/2)\Vert x^+ - y^+\Vert^2$}
                        \STATE{\textbf{break}}
                    \STATE{$L^+ := 2^{i}L$}
                \STATE{\textbf{Return:} $y^+, x^+, \alpha^+, L^+$}
                \caption{Armijo Line Search}
        \begin{algorithm}[H]\label{alg:chambolle-btls}
                    % \textbf{Function ChamBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)
                    \textbf{Function ChamBT input: }
                    \begin{tabular}{ll}
                        $f:\RR^n \rightarrow \RR$ & Convex Lipschitz smooth\\ 
                        $g:\RR^n \rightarrow \overline\RR$ & Convex with Proximal Operator\\ 
                        $x\in \RR^n$ & Vector\\
                        $v\in \RR^n$ & Vector\\
                        $\alpha \in \RR$ & Vector\\
                        $L\in \RR$ & Number, $L > 0$ \\
                        $L_{\min} \in \RR$ & Number, $L_{\min} > 0$\\
                        $\rho \in \RR$ & Number, $\rho \in (0, 1)$\\
                    \end{tabular}
                \STATE{$L^+ := \max(L_{\min}, \rho L)$.}
                \FOR{$i = 1, 2, \ldots, 53$}
                    \STATE{$\alpha^+ := (1/2)\left(\alpha\sqrt{\alpha^2 + L/L^+} - \alpha^2\right)$. }
                    \STATE{$y^+ := \alpha^+ v + (1 - \alpha^+) x$. }
                    \STATE{$x^+ := T_{1/L^+, f, g}(y^+)$.}
                    \IF{$2D_f(x^+, y^+) \le \Vert x^+ - y^+\Vert^2$}
                        \STATE{\textbf{break}}
                    \STATE{$L^+ := 2^iL^+$.}
                \STATE{\textbf{Return: }$y^+, x^+, \alpha^+, L^+$}
                \caption{Chambolle's Backtracking}
        \begin{algorithm}[H]\label{alg:beck-mono}
                    % \textbf{Function BeckMono}($f, g, x, v, L, L_{\min}, \rho, \alpha$)
                    \textbf{Function BeckMono Input:}
                    \begin{tabular}{ll}
                        $f: \RR^n \rightarrow \RR$ & \\
                        $g: \RR^n \rightarrow \overline \RR$ & \\
                        $\tilde x \in \RR^n$ & \\
                        $x \in \RR^n$ & 
                    \end{tabular}

@@

                            \STATE{$\tilde x_{k + 1} := T_{L_0^{-1}}y_k$.}

@@

    \section{Practical enhancement from the Nesterov's Monotone Variant}
        Firstly, we will introduce some theories in for nonconvex functions. 
        The following assumption will characterize the full scope of discussion in nonconvexity objective function.

    \section{Restarting with function values}
    \section{Applying them to large scale LP}
    \section{Nonconvex convergence}

>>>>

@@

                0 &\le F(z) - F(\bar x) + \frac{L}{2}\Vert z - x\Vert^2 - \frac{L}{2}\Vert z - \bar x\Vert^2. 

@@

                \Vert \mathcal G_{1/L_k} y_k\Vert 

@@

                &= -\alpha_k^{-1}L_k^{-1}(\mathcal G_{1/L_k}(y_k)). 

@@

            For all $k \ge 1$ let $\hat L_k = \max_{i = 0, 1, \ldots, k} L_i$ then 

@@

                    \frac{\alpha_0 \sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{\hat L^{-1}_k}

@@

                    1 + \frac{1}{2}\alpha_0 \sqrt{L_0}k\sqrt{\hat L^{-1}_k}

@@

                    1 + \frac{k\alpha_0\sqrt{L_0 \hat L^{-1}_k}}{2}

@@

                    \sqrt{L_0^{-1}\hat L_k} + \frac{k\alpha_0}{2}

@@

                L^{-1}_0\hat L_k\left(

@@

                = \frac{4\hat L_k}{L_0(2 + k \alpha_0)^2}. 

@@

            The above inequality would work the same if we set: 
                \hat L_k &= \max\left(
                    L_0, \frac{1}{k} \sum_{i = 1}^{k} \sqrt{L_i^{-1}}

@@

    \section{Algorithmic description of GMAPG}
        There are several components to the GMAPG algorithm. 
        This section will introduce various type of implementations that can be fitted into GMAPG in Definition \ref{def:generic-mapg-ls}. 
        \begin{algorithm}[H]
            {\small
            \begin{algorithmic}[1]\label{alg:armijo-ls}
                \STATE{\noindent
                    % \textbf{Function ArmijoLS}
                    % $(f, g, x, v, L, \alpha, \_, \_)$
                    \textbf{Function ArmijoLS:}
                    \begin{tabular}{ll}
                        $f : \RR^n \rightarrow \RR$ & Convex Lipschitz smooth\\ 
                        $g: \RR^n \rightarrow \overline \RR$  &  Convex function with Proximal operator\\ 
                        $x \in \RR^n$ & Vector\\
                        $v \in \RR^n$ & Vector\\
                        $L \in \RR$ & $L > 0$\\
                        $\alpha \in \RR$  & $\alpha \in (0, 1]$
                    \end{tabular}
                }
                \STATE{$\alpha^+ := (1/2)\left(\alpha\sqrt{\alpha^2 + 1} - \alpha^2\right)$.}
                \STATE{$y^+ := \alpha^+ v + (1 - \alpha^+)x$.}
                \STATE{$L^+ := L$. }
                \FOR{$i = 1, 2,\ldots, 53$}
                    \STATE{$L^+ := 2L^+$. }
                    \STATE{$x^+ := T_{1/L^+, f, g}(y^+)$. }
                    \IF{$D_f(x^+, y^+) \le (L^+/2)\Vert x^+ - y^+\Vert^2$}
                        \STATE{\textbf{break}}
                    \ENDIF
                    \STATE{$L^+ := 2^{i}L$}
                \ENDFOR
                \STATE{\textbf{Return:} $y^+, x^+, \alpha^+, L^+$}
                \caption{Armijo Line Search}
            \end{algorithmic}
            }
        \end{algorithm}
        \begin{algorithm}[H]\label{alg:chambolle-btls}
            {\small
            \begin{algorithmic}[1]
                \STATE{\noindent
                    % \textbf{Function ChamBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)
                    \textbf{Function ChamBT input: }
                    \begin{tabular}{ll}
                        $f:\RR^n \rightarrow \RR$ & Convex Lipschitz smooth\\ 
                        $g:\RR^n \rightarrow \overline\RR$ & Convex with Proximal Operator\\ 
                        $x\in \RR^n$ & Vector\\
                        $v\in \RR^n$ & Vector\\
                        $\alpha \in \RR$ & Vector\\
                        $L\in \RR$ & Number, $L > 0$ \\
                        $L_{\min} \in \RR$ & Number, $L_{\min} > 0$\\
                        $\rho \in \RR$ & Number, $\rho \in (0, 1)$\\
                    \end{tabular}
                }
                \STATE{$L^+ := \max(L_{\min}, \rho L)$.}
                \FOR{$i = 1, 2, \ldots, 53$}
                    \STATE{$\alpha^+ := (1/2)\left(\alpha\sqrt{\alpha^2 + L/L^+} - \alpha^2\right)$. }
                    \STATE{$y^+ := \alpha^+ v + (1 - \alpha^+) x$. }
                    \STATE{$x^+ := T_{1/L^+, f, g}(y^+)$.}
                    \IF{$2D_f(x^+, y^+) \le \Vert x^+ - y^+\Vert^2$}
                        \STATE{\textbf{break}}
                    \ENDIF
                    \STATE{$L^+ := 2^iL^+$.}
                \ENDFOR
                \STATE{\textbf{Return: }$y^+, x^+, \alpha^+, L^+$}
                \caption{Chambolle's Backtracking}
            \end{algorithmic}
            }
        \end{algorithm}
        \begin{algorithm}[H]\label{alg:beck-mono}
            \begin{algorithmic}[1]
                \STATE{\noindent
                    \textbf{Function BeckMono Input:}
                    \begin{tabular}{ll}
                        $f: \RR^n \rightarrow \RR$ & \\
                        $g: \RR^n \rightarrow \overline \RR$ & \\
                        $\tilde x \in \RR^n$ & \\
                        $x \in \RR^n$ & 
                    \end{tabular}

@@

                \STATE{\textbf{Return: } $x^+$}

@@

                            \STATE{$\tilde x_{k + 1} := T_{L_k^{-1}}y_k$.}

@@

    \section{Practical enhancement from the Nesterov's Monotone Variant}
        Firstly, we will introduce some theories in for nonconvex functions. 
        This is necessary because Nesterov's monotone variants can adapt to weakly convex objective functions. 
        The following assumption will characterize the full scope of discussion in nonconvexity objective function. 
        \begin{definition}[nonconvex Nesterov's monotone scheme]\label{def:nes-monotone-scheme}

        \end{definition}
    \section{Restarting with function values}
    \section{Applying them to large scale LP}
